\subsection{Gelatin Hydrogel Particles}
%Gelatin as a hydrogel material (stability, biocompatibility, critical gelation concentration, and cross-linking) - maybe some of it in stoa

Gelatin is a denatured protein obtained by hydrolysis of collagen and has an average size of 20 -- 200 kDa. Gelatin is divided in to two categories type A and type B, depending on the origin of the collagen and the manner of extraction. Type A gelatin is extracted from porcine skin collagen via acidic hydrolysis and type B from bovine collagen via alkaline hydrolysis. \parencite{ChangPreparationAndChar2014, Hong2020ProteinBasedNanoparticles,Xing2014IncreasingMechanicalStrength}

Hydrogels formed by gelatin are composed of gelatin molecules aggregated into triple helices and are both biocompatible and biodegradable. These physically cross-linked gelatin hydrogels can be formed at concentrations above 2\%w/v, but have low mechanichal strength and decompose at higher temperatures --- 30--35\si{\degreeCelsius} --- thus if used at physiological conditions, other manners of cross-linking are needed. \parencite{ChangPreparationAndChar2014, Hong2020ProteinBasedNanoparticles,Xing2014IncreasingMechanicalStrength}

A method for increasing the stability of gelatin hydrogels is covalently cross-linking the hydrogel utilising a cross-linking agent such as glutaraldehyde \parencite{Hong2020ProteinBasedNanoparticles,Xing2014IncreasingMechanicalStrength}.
When used as a cross-linking agent at neutral to slightly alkaline conditions, the carbonyl groups of glutaraldehyde reacts with the amino groups of the gelatin side chains yielding a stable amide bond between the compounds. Approximately five percent of the amino acids of gelatin are basic, and as such available for cross-linking. Moreover it should be noted that molecules of glutaraldehyde can form a product with them selves, resulting in the removal of pure glutaraldehyde from the solution. 
\parencite{ChangPreparationAndChar2014, Farris2010AlternativeRecationMechanism} 

%evt billede af glutaraldehyd og gelatine + 2xglutaraldehyd

For drug delivery proposes glutaraldehyd cross-linked gelatin hydrogel particles have been prepared via several methods including desolvation method\parencite{Hong2020ProteinBasedNanoparticles}, mechanical stirring\parencite{Cascone2002GelatinNanoparticlesWOemul}, and via microfluidic devices\parencite{Zhang2019GelatinCages}.  
\newpage


    